An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2015-01-07 mixedwindow.tex
Minor tweaks to text and exposition

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Ken West, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

\begin{abstract}
  \noindent This paper develops a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
  using a recursive window to estimate the benchmark model but a
  fixed-length rolling window to estimate the alternative. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic, without
  affecting the asymptotic distribution of this test statistic.  The
  paper also presents Monte Carlo evidence that this statistic has
  much higher power than existing out-of-sample statistics in a common
  use-case for these tests: when the \dgp\ is subject to instability.
  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
  and supports their finding that the equity premium is unpredictable
  out-of-sample.

@@

\noindent Keywords: Forecast Evaluation, Martingale Difference
Sequence, Model Selection

@@

This paper proposes an out-of-sample (\oos) test statistic that is
asymptotically normal and correctly centered even when the models
studied are nested. The test is based on one proposed by
\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
with a recursive window and the alternative models with a fixed length
rolling window. The rolling window ensures asymptotic normality, as in
\citet{GiW:06}, and the recursive window allows the null hypothesis to
be a statement about the specification of the Data Generating Process,
which is the focus of the vast majority of the \oos\ testing
literature.%
\footnote{In particular, this is the focus of \citet{Wes:96},
  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
  many others but not \citet{GiW:06}. See \citet{Wes:06} and
  \citet{ClM:13} for a thorough overview of this literature.} %
This combination of estimation windows also gives our test statistic
high power against alternative \dgp s that cause the benchmark model
to be unstable --- structural breaks, time-varying coefficients, or
forms of nonlinearity, for example --- which is a common motivation
for using these tests.

\oos\ tests are common in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a Martingale Difference Sequence (\mds).  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.} %

However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present Monte Carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal with mean zero when the benchmark model is a
random walk \citep{ClW:06}. Estimating the parameters of the smaller
model invalidates their proof.

This paper shows that a modified version of their statistic is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, the pseudotrue benchmark model must be estimated
consistently, but the larger alternative model must continue to be
estimated inconsistently so that the test statistic is not degenerate
when the models are nested. We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.
This approach has the further advantage over existing \oos\ tests for
nested models that the alternative can be essentially arbitrary as
long as high level moment conditions hold. In particular, researchers
can use model selection techniques like the \aic\ or \bic\ to
determine the number of lags to include, the particular exogenous
variables to include, etc. Moreover, although we focus on nested
models in this paper, the approach can be used with non-nested models
as well. As \citet{ClM:11b} have recently pointed out,
\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
the benchmark and alternative models, which is allowable under the
null. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')

The next section presents the intuition and theory for our new statistic.
Section~\ref{sec:2} presents
simulations that compare our pairwise \oos\ test to \poscw\ original
statistics and Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability and Section~\ref{sec:4} concludes. Proofs of
our results have been put in a separate Appendix along with
some supporting results \citep{Cal:14b}.

@@

This section presents the new \oos\ statistic; first we give an
informal motivation of the statistc, then present the paper's key
assumptions in section~\ref{sec:1a} and present our formal theoretical
results in section~\ref{sec:1b}.

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$, that $v_t$ is another random process that is believed to
potentially contain information about $y_{t+1}$, and that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value
and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
\end{equation}
almost surely.

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In their 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
their 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimators of $\btrue$ do not converge to $\btrue$.

@@

This overview has presented an especially simple version of the result
to make the intuition as clear as possible. The next section lists the
specific assumptions for the more general case.

@@

The \dgp\ has three different parametrizations: one to study the
tests' size, one to study power under stationarity, and one to study
power if there is a single break in the relationship between the
target and predictors.  The \dgp\ is:
\begin{align*}
  y_t &= \gamma_{1t} + \gamma_{2t} z_{t-1} + e_t &
  \gamma_t &=
  \begin{cases}
    (0.5, 0)    & \text{size simulations} \\
    (0.5, 0.35) & \text{power (stable)} \\
    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
  \end{cases}\\\nonumber
  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
\end{align*}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
pricing application similar to \citepos{GoW:08} which we study in
Section~\ref{sec:3}.

@@

Table~\ref{tab:mc1} presents the simulation results.  For all of the
stable parameter values, the proposed new statistic has similar
rejection probability to \citepos{ClW:07}.  Both of Clark and West's
tests are generally slightly undersized relative to our new test,
which is itself slightly undersized: when $R$ is 120 and $P$ is 360
our test statistic has size 7.6\% and Clark and West's rolling and
recursive window tests have size 7.5\% and 6.2\% respectively, at a
nominal size of 10\%.  For the stable alternative, our new statistic
typically has slightly higher power than Clark and West's rolling
window and lower power than their recursive window.  For example, when
$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
our statistic at 73.0\%, and the recrusive window statistic at 82.3\%,
again for a nominal size of 10\%.  In general, the statistics perform
similarly under stability.

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\begin{equation*}
  \mathit{excess~return}_{t} = \alpha_{0} + \alpha_{1}\
  \mathit{predictor}_{t-1} + \ep_{t},
\end{equation*}
where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

\begin{table}[tb!]
  \centering
  \empiricaltable
\caption{Results from \oos\ comparison of equity premium prediction
  models; the benchmark is the recursive sample mean of the equity
  premium and each alternative model is a constant and single lag of
  the variable listed in the ``predictor'' column.  The dataset begins
  in 1927 and ends in 2009 and is annual data. The ``value'' column
  lists the value of this paper's \oos\ statistic, the ``naive''
  column indicates whether the statistic is significant at standard
  critical values, and the ``corrected'' column indicates significance
  using critical values that
  account for the number of models.  See Section~\ref{sec:3} for details.}
\label{tab:em1}
\end{table}

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' indicates whether the statistic is greater than the
standard \bootsize\% critical value (\naivecriticalvalue) Three
predictors are
significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio.

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance. A
full treatment of this issue is beyond the scope of this paper,
however, it is straightforward to use Theorem~\ref{res:1} and
Lemma~\ref{lem:2} to derive an appropriate critical value as
in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \sigma^2)$ under
the \mds\ null hypothesis, the continuous mapping theorem implies that
$\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
\sim N(0, D^{-1/2} \sigma^2 D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \sh
\hat D^{-1/2})$ distribution to generate a critical value for the
\emph{largest} individual test statistic under the null ---
\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
this critical value, none of the predictors are siginificant at
\bootsize\%.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here. Moreover, I need to
  explain why it's not a concern for these statistics in general.} %

\section{Discussion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window --- as do Clark and West --- but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test when the \dgp\ is stable but can have much higher power when the
\dgp\ has structural breaks.

>>>>

\author{Gray Calhoun\thanks{Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

\begin{abstract}
  \noindent This paper develops a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
  using a recursive window to estimate the benchmark model but a
  fixed-length rolling window to estimate the alternative. The
  resulting statistic is asymptotically normal even when the models
  are nested. The
  paper also presents Monte Carlo evidence that this statistic has
  much higher power than existing out-of-sample statistics in a common
  use-case for these tests: when the \dgp\ is subject to instability.
  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
  and supports their finding that the equity premium is unpredictable
  out-of-sample.

@@

\noindent Keywords: Forecast Evaluation, Martingale Difference
Sequence, Model Selection, Forecast Encompassing

@@

This paper proposes an out-of-sample (\oos) test statistic that is
asymptotically normal and correctly centered even when the models
studied are nested. The test is based on one proposed by
\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
with a recursive window and the alternative models with a fixed length
rolling window. The rolling window ensures asymptotic normality, as in
\citet{GiW:06}, and the recursive window allows the null hypothesis to
be a statement about the specification of the Data Generating Process,
which is the focus of the vast majority of the \oos\ testing
literature.%
\footnote{In particular, this is the focus of \citet{Wes:96},
  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
  many others but not \citet{GiW:06}. See \citet{Wes:06} and
  \citet{ClM:13} for a thorough overview of this literature.} %
This combination of estimation windows also gives our test statistic
high power against alternatives that cause the benchmark model
to be unstable --- structural breaks, time-varying coefficients, or
forms of nonlinearity, for example --- which is a common motivation
for using these tests.

\oos\ tests are common in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a Martingale Difference Sequence (\mds).  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic to have mean-zero under the null.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.} %
However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present Monte Carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal with mean zero when the benchmark model is a
random walk \citep{ClW:06}. Estimating the parameters of the smaller
model invalidates their proof.

This paper proposes a modified version of their statistic and shows that it is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, the pseudotrue benchmark model must be estimated
consistently, but the larger alternative model must continue to be
estimated inconsistently so that the test statistic is not degenerate
when the models are nested. We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.
This approach has the further advantage over existing \oos\ tests for
nested models that the alternative can be essentially arbitrary as
long as high level moment conditions hold. In particular, researchers
can use model selection techniques like the \aic\ or \bic\ to
determine the number of lags to include, the particular exogenous
variables to include, etc. Moreover, although we focus on nested
models in this paper, the approach can be used with non-nested models
as well. As \citet{ClM:11b} have recently argued,
\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
the benchmark and alternative models, which is allowable under the
null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')

The next section presents the intuition and theory for our new
statistic.  Section~\ref{sec:2} presents simulations that compare our
pairwise \oos\ test to \poscw\ original statistics.
Section~\ref{sec:3} demonstrates the use of our statistic by
reanalyzing \citepos{GoW:08} study of excess return predictability and
demonstrates how our results can be used in settings with many
alternative models. Section~\ref{sec:4} concludes. Proofs of our
results have been put in a separate Appendix along with some
supporting results \citep{Cal:15}.

@@

This section presents the new \oos\ statistic; first we give an
informal motivation of the statistic, then present the paper's key
assumptions in Section~\ref{sec:1a} and present our formal theoretical
results in Section~\ref{sec:1b}.

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$, that $v_t$ is another random process that is believed to
potentially contain information about $y_{t+1}$, and that
$(y_t, x_t, v_t)$ is stationary and weakly dependent.
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient for the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
with $R$ an arbitrary starting value
and $P = T - R$.

Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
\end{equation}
almost surely.
\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$,%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
and $R$ is kept finite as $T \to \infty$ so that
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window prevents
the degeneracy that can arise when comparing nested models out-of-sample (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the \oos\ average remains positive and the average obeys a \clt.%
\footnote{This approach was first introduced by \citet{GiW:06}.} %

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In their 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
rolling window as the $\yh_{t+1}$. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimators of $\btrue$ do not converge to $\btrue$.

@@

So far, we have presented an especially simple version of the result
to make the intuition as clear as possible. The next section lists the
specific assumptions for the more general case and defines additional notation.

@@

The \dgp\ has three different parametrizations: one to study the
tests' size, one to study power under stationarity, and one to study
power if there is a single break in the relationship between the
target and predictors.  The \dgp\ is:
\begin{align*}
  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
  \gamma_t &=
  \begin{cases}
    (0.5, 0)    & \text{size simulations} \\
    (0.5, 0.35) & \text{power (stable)} \\
    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
  \end{cases}\\\nonumber
  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
\end{align*}
Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
on a constant, and the alternative regresses $y_{t+1}$ on a constant and
$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
pricing application similar to \citepos{GoW:08} which we study in
Section~\ref{sec:3}.

@@

Table~\ref{tab:mc1} presents the simulation results.  For all of the
stable parameter values, the proposed new statistic has similar
rejection probability to \citepos{ClW:07}.  Both of Clark and West's
tests are generally slightly undersized relative to our new test,
which is itself slightly undersized: when $R$ is 120 and $P$ is 360
our test statistic has size 7.6\% and Clark and West's rolling and
recursive window tests have size 7.5\% and 6.2\% respectively, at a
nominal size of 10\%.  For the stable alternative, our new statistic
typically has slightly higher power than Clark and West's rolling
window and lower power than their recursive window.  For example, when
$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
again for a nominal size of 10\%.  In general, the statistics perform
similarly under stability.

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\begin{equation*}
  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
  \mathit{predictor}_{t} + \ep_{t+1},
\end{equation*}
where $\beta_{0}$ and
$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the \emph{predictor} column of
Table~\ref{tab:em1}. \citep[See][for a detailed description of the
variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

\begin{table}[tb!]
  \centering
  \empiricaltable
\caption{Results from \oos\ comparison of equity premium prediction
  models; the benchmark is the recursive sample mean of the equity
  premium and each alternative model is a constant and single lag of
  the variable listed in the \emph{predictor} column.  The dataset begins
  in 1927 and ends in 2009 and is annual data. The \emph{value} column
  lists the value of this paper's \oos\ statistic, the \emph{naive}
  column indicates whether the statistic is significant at standard
  critical values, and the \emph{corrected} column indicates significance
  using critical values that
  account for the number of models.  See Section~\ref{sec:3} for details.}
\label{tab:em1}
\end{table}

Table~\ref{tab:em1} presents the results for each model.  The column
\emph{value} gives the value of the test statistic for each model,
while \emph{naive} indicates whether the statistic is greater than the
standard 10\% critical value (\naivecriticalvalue). Three predictors
are significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio, and the median forecast is significant as well.
This could suggest that excess returns are not an \mds\ and that
information in these three variables is useful for predicting returns.

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance.
There are several approaches that could accommodate this multiplicity, and a full
treatment is beyond the scope of this paper, however, it is
straightforward to use Theorem~\ref{res:1} and Lemma~\ref{lem:2} to
derive an appropriate critical value similar to~\citet{Whi:00}.

Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
multivariate $f_t$, so the continuous mapping theorem implies that
\begin{equation*}
  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
\end{equation*}
where $W \sim N(0, V)$ and $V$ is the $\nmod
\times \nmod$ correlation matrix with elements
\begin{equation*}
  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
\end{equation*}

To estimate $V$, we use the correlation matrix associated with the
multivariate analogue of $\sigmah_2$,
\[
\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
\]
where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
\begin{gather*}
  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
  \intertext{and}
  \gh_{it} = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{i,s+1}) x_s'\Bigg]\,
            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
\end{gather*}
respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
$1 - \alpha$ quantile of the distribution of $\max_i \hat W_i$, with
$\hat W \sim N(0, \hat V)$.  Then
\begin{equation*}
  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{1i} > \hat c\Big] \leq \alpha,
\end{equation*}
under the null hypothesis that excess returns are an \mds\ with
respect to all of the information contained in the variables listed in
Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
value.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here.} %

We calculate $\hat c$ by generating \empiricaldraws\ draws from
$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
remain significant at 10\% using this critical value. Using this
critical value, none of the predictors are significant at 10\%, which
gives additional support to \citepos{GoW:08} conclusion that excess
returns are unpredictable and also demonstrates the importance of
correcting for multiplicity in these studies.

\section{Discussion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window --- as do Clark and West --- but
estimating the benchmark model with a recursive window.  Simulations
indicate that the new statistic behaves similarly to Clark and West's
original test when the \dgp\ is stable but can have much higher power
when the \dgp\ has structural breaks. We also have presented an
empirical study of the equity premium that demonstrates how to use
these results with several alternative models.
